Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-22 ms.tex
filling in the introduction

% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
The \PLANCK~mission \citep{planck2013,planck2015} has recently provided a 
breakthrough in full-sky mapping of emission from interstellar dust, by 
obtaining relatively artifact free, full-sky maps in nine bandpasses from QQ to
PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and high 
sensitivity. Although these \PLANCK~maps contain various emission components, 
including the CMB, zodiacal light,and molecular emission, it is nevertheless 
possible to isolate exquisite maps of thermal emission from interstellar dust 
grains.
% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.

@@

% list of the sections
Much of our detailed methodology is identical to that of Meisner/Finkbeiner 
2015. As a result, throughout this paper, we mainly emphasize any notable 
differences relative, and otherwise refer the reader to Meisner/Finkbeiner 
2015 for thorough details.

>>>>

% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
The \PLANCK~mission \citep{planck2013,planck2015} has recently provided a 
breakthrough in full-sky mapping of emission from interstellar dust, by 
obtaining relatively artifact free, full-sky maps in nine bandpasses from 30 
GHz to 857 GHz, with a superb combination of very high sensitivity and 
near-\IRAS~resolution from 217 GHz to 857 GHz. Although these \PLANCK~maps 
contain a superposition of various emission components, including the CMB, 
compact sources, and molecular emission, it is nevertheless possible to isolate
exquisite maps of thermal emission from interstellar dust grains.

% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. For many years, the 
\citet[hereafter SFD]{SFD} dust map has been the industry standard for 
predicting Galactic reddening. The SFD reddening predictions rely on the
\IRAS~100$\mu$m dust emission map as a $6.1'$ FWHM template for dust optical 
depth, after modulating the emission by a $1.3^{\circ}$ FWHM temperature 
correction based on the DIRBE 140$\mu$m/240$\mu$m ratio, assuming the dust
emits as a $\beta$=2 modified blackbody (MBB). \citet[henceforth FDS99]{FDS99} 
combined the \IRAS/DIRBE data sets used by SFD with the FIRAS \citep{firas} 
dust spectra from 100-3000 GHz to extrapolate thermal dust emission from 
\IRAS~wavelengths to CMB frequencies. FDS99 found that no single MBB could
adequately fit the relatively sharp peak of the dust spectral energy 
distribution (SED) while also capturing the spectrum's flattening toward
millimeter wavelengths. FDS99 therefore fit the dust SED with a linear 
combination of two MBBs, which can be thought of as representing two 
distinct grain species in equilibrium with the same ISRF.

Both SFD/FDS99 DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.

@@

% list of the sections
Much of our detailed methodology is identical to that of \cite{meisner15}. As a
result, throughout this paper, we mainly emphasize any notable differences 
relative to this previously published work, and otherwise refer the reader to 
\cite{meisner15} for thorough details.
